JAGS Model

### 2020-02-19 Rcodes/JAGS_overdoses.Rmd
trimmed the rmd

ggplot()+geom_point(aes(x=o_t_values$month, y=o_t_values$o_t),color='red')+geom_boxplot(aes(x=month,y=o_t),data = df_o_t)
```

@@

```{r eval=FALSE, include=FALSE}
plot(ppc)
```

@@

test <- as.matrix(df_u_t)
colnames(test) <- seq(1,12)
head(test)
mtx_u_t <- as.data.frame(test)
head(mtx_u_t)

df_u_t <- gather(mtx_u_t, key = 'month',value = 'u_t')
head(df_u_t)

df_u_t$month <- factor(df_u_t$month,levels = seq(1,12))
str(df_u_t)

@@

@@

test <- as.matrix(df_x_a)
colnames(test) <- seq(1,12)
head(test)
mtx_x_a <- as.data.frame(test)
head(mtx_x_a)

df_x_a <- gather(mtx_x_a, key = 'month',value = 'x_a')
head(df_x_a)

df_x_a$month <- factor(df_x_a$month,levels = seq(1,12))
str(df_x_a)

>>>>

ggplot()+geom_point(aes(x=o_t_values$month, y=o_t_values$o_t),color='red')+geom_boxplot(aes(x=month,y=o_t),data = df_o_t)
```
### Predictive Posterior Checks

@@

```{r eval=FALSE, include=FALSE}
plot(ppc)
```
### $U_t$: Predictive Posterior Checks

@@

test <- as.matrix(df_u_t)
colnames(test) <- seq(1,12)
mtx_u_t <- as.data.frame(test)

df_u_t <- gather(mtx_u_t, key = 'month',value = 'u_t')

df_u_t$month <- factor(df_u_t$month,levels = seq(1,12))

@@

### $x_A$: Predictive Posterior Checks

@@

test <- as.matrix(df_x_a)
colnames(test) <- seq(1,12)

mtx_x_a <- as.data.frame(test)

df_x_a <- gather(mtx_x_a, key = 'month',value = 'x_a')

df_x_a$month <- factor(df_x_a$month,levels = seq(1,12))
